Toward early-warning detection of gravitational waves from compact binary coalescence

### 2014-05-06 article.tex
Switch to emulateapj
Remove unnecessary macro

\documentclass[preprint2]{aastex}

\usepackage[colorlinks]{hyperref}
\usepackage{epstopdf}
\usepackage{amsmath,amsthm}
\usepackage{stmaryrd} % For \shortuparrow and \shortdownarrow
\usepackage{upgreek} % For \upmu, upright mu
\usepackage{multirow}

@@

\newcommand{\earlywarning}{early-warning}
\newcommand{\NS}{NS}
\newcommand{\mbta}{MBTA}
\newcommand{\GW}{GW}%{{\sc gw}}
\newcommand{\EM}{EM}%{{\sc em}}
\newcommand{\GRB}{GRB}%{{\sc grb}}
\newcommand{\CBC}{CBC}%{{\sc cbc}}
\newcommand{\LIGO}{LIGO}%{{\sc ligo}}
\newcommand{\LCGT}{LCGT}%{{\sc lcgt}}
\newcommand{\GEO}{GEO600}%{{\sc geo600}}
\newcommand{\LSO}{LSO}%{{\sc lso}}
\newcommand{\SNR}{S/N}%{{\sc snr}}
\newcommand{\realtime}{real-time}
\newcommand{\Msun}{\ensuremath{M_{\odot}}}
\newcommand{\order}[1]{\ensuremath{\mathcal{O}[#1]}}
\newcommand{\tmpsamps}{\ensuremath{N}}
\newcommand{\numtmps}{\ensuremath{M}}
\newcommand{\numslices}{\ensuremath{S}}
% macros for number of svd basis functions
\newcommand{\SVD}{SVD}%{{\sc svd}}
\newcommand{\svdtmps}[1]{\ensuremath{L^#1}}
\newcommand{\numsvdtmps}{\svdtmps{s}}
% macros for sample points in slices
\newcommand{\slicesamps}[1]{\ensuremath{N^#1}}
\newcommand{\slicessamps}{\slicesamps{s}}
\newcommand{\fftblock}{\ensuremath{D}}
\newcommand{\resampsamps}{\ensuremath{N^\shortdownarrow,\, N^\shortuparrow}}
\newcommand{\fir}{FIR}%{{\sc fir}}
\newcommand{\fft}{FFT}%{{\sc fft}}
\newcommand{\fmax}{\ensuremath{f^0}}
\newcommand{\flops}{flop~s$^{-1}$}
\newcommand{\gstlal}{{\tt gstlal}}
\newcommand{\gstreamer}{GStreamer}
\newcommand{\numcpus}{{600}}
\newcommand{\lloid}{LLOID}%{{\sc lloid}}
\newcommand{\TD}{TD}%{{\sc td}}
\newcommand{\FD}{FD}%{{\sc fd}}

@@

\title{Toward \earlywarning\ detection of gravitational waves from compact binary coalescence}

@@

\section{Prospects for \earlywarning\ detection and \EM\ follow-up}

@@

In this section, we describe a decomposition of the \CBC\ signal space that
reduces \TD\ filtering cost sufficiently to allow for the
possibility of \earlywarning\ detection with modest computing requirements.  We
expand on the ideas of \citet{Marion2004} and \citet{Buskulic2010} that describe a
multi-band decomposition of the compact binary signal space that resulted in
a search with minutes latency during S6/VSR3~\citep{HugheyGWPAW2011}.  We combine this
with the \SVD\ rank-reduction method of \citet{Cannon:2010p10398} that exploits
the redundancy of the template banks.

>>>>

\documentclass[iop,apj]{emulateapj}
\usepackage{apjfonts}

\usepackage[colorlinks]{hyperref}
\usepackage{amsmath,amsthm}
\usepackage{stmaryrd} % For \shortuparrow and \shortdownarrow
\usepackage{upgreek} % For \upmu, upright mu
\usepackage{multirow}

@@

\newcommand{\NS}{NS}
\newcommand{\mbta}{MBTA}
\newcommand{\GW}{GW}%{{\sc gw}}
\newcommand{\EM}{EM}%{{\sc em}}
\newcommand{\GRB}{GRB}%{{\sc grb}}
\newcommand{\CBC}{CBC}%{{\sc cbc}}
\newcommand{\LIGO}{LIGO}%{{\sc ligo}}
\newcommand{\LCGT}{LCGT}%{{\sc lcgt}}
\newcommand{\GEO}{GEO600}%{{\sc geo600}}
\newcommand{\LSO}{LSO}%{{\sc lso}}
\newcommand{\SNR}{S/N}%{{\sc snr}}
\newcommand{\realtime}{real-time}
\newcommand{\Msun}{\ensuremath{M_{\odot}}}
\newcommand{\order}[1]{\ensuremath{\mathcal{O}[#1]}}
\newcommand{\tmpsamps}{\ensuremath{N}}
\newcommand{\numtmps}{\ensuremath{M}}
\newcommand{\numslices}{\ensuremath{S}}
% macros for number of svd basis functions
\newcommand{\SVD}{SVD}%{{\sc svd}}
\newcommand{\svdtmps}[1]{\ensuremath{L^#1}}
\newcommand{\numsvdtmps}{\svdtmps{s}}
% macros for sample points in slices
\newcommand{\slicesamps}[1]{\ensuremath{N^#1}}
\newcommand{\slicessamps}{\slicesamps{s}}
\newcommand{\fftblock}{\ensuremath{D}}
\newcommand{\resampsamps}{\ensuremath{N^\shortdownarrow,\, N^\shortuparrow}}
\newcommand{\fir}{FIR}%{{\sc fir}}
\newcommand{\fft}{FFT}%{{\sc fft}}
\newcommand{\fmax}{\ensuremath{f^0}}
\newcommand{\flops}{flop~s$^{-1}$}
\newcommand{\gstlal}{{\tt gstlal}}
\newcommand{\gstreamer}{GStreamer}
\newcommand{\numcpus}{{600}}
\newcommand{\lloid}{LLOID}%{{\sc lloid}}
\newcommand{\TD}{TD}%{{\sc td}}
\newcommand{\FD}{FD}%{{\sc fd}}

@@

\title{Toward early-warning detection of gravitational waves from compact binary coalescence}

@@

\section{Prospects for early-warning detection and \EM\ follow-up}

@@

In this section, we describe a decomposition of the \CBC\ signal space that
reduces \TD\ filtering cost sufficiently to allow for the
possibility of early-warning detection with modest computing requirements.  We
expand on the ideas of \citet{Marion2004} and \citet{Buskulic2010} that describe a
multi-band decomposition of the compact binary signal space that resulted in
a search with minutes latency during S6/VSR3~\citep{HugheyGWPAW2011}.  We combine this
with the \SVD\ rank-reduction method of \citet{Cannon:2010p10398} that exploits
the redundancy of the template banks.
